---
title: "PM566-lab10-Tiansheng-Jin"
author: "Tiansheng Jin"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```

```{r set-up}
# install.packages(c("RSQLite", "DBI"))
# if (!require(RSQLite)) install.packages(c("RSQLite"))
# if (!require(DBI)) install.packages(c("DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)

dbListTables(con)
```

```{sql, connection=con}
PRAGMA table_info(actor)
```

```{r}
dbGetQuery(con,
           "PRAGMA table_info(actor)")
```

# Exercise 1

Retrive the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.

```{r}
dbGetQuery(con, "
 SELECT actor_id, first_name, last_name
 FROM actor
 ORDER by last_name, first_name
 LIMIT 10
             ")
```

Try in SQL

```{sql, connection=con}
SELECT actor_id, first_name, last_name
FROM actor
ORDER by last_name, first_name
```

# Exercise 2

Retrive the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.

```{sql, connection=con}
SELECT actor_id, first_name, last_name
FROM actor
WHERE last_name IN ('WILLIAMS', 'DAVIS')
ORDER by last_name
```

# Exercise 3

Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.

SELECT DISTINCT 
FROM 
WHERE date(___) = '2005-07-05'

# Exercise 4

Exercise 4.1
Construct a query that retrives all rows from the payment table where the amount is either 1.99, 7.99, 9.99.

SELECT *
FROM ___
WHERE ___ IN (1.99, 7.99, 9.99)
Exercise 4.2
Construct a query that retrives all rows from the payment table where the amount is greater then 5

SELECT *
FROM 
WHERE 
Exercise 4.2
Construct a query that retrives all rows from the payment table where the amount is greater then 5 and less then 8

SELECT *
FROM ___
WHERE ___ AND ___

# Exercise 5

Retrive all the payment IDs and their amount from the customers whose last name is ‘DAVIS’.

SELECT 
FROM 
  INNER JOIN 
WHERE 
AND 

# Exercise 6

Exercise 6.1
Use COUNT(*) to count the number of rows in rental

Exercise 6.2
Use COUNT(*) and GROUP BY to count the number of rentals for each customer_id

Exercise 6.3
Repeat the previous query and sort by the count in descending order

Exercise 6.4
Repeat the previous query but use HAVING to only keep the groups with 40 or more.

# Exercise 7
The following query calculates a number of summary statistics for the payment table using MAX, MIN, AVG and SUM

Exercise 7.1
Modify the above query to do those calculations for each customer_id

Exercise 7.2
Modify the above query to only keep the customer_ids that have more then 5 payments

# Cleanup
Run the following chunk to disconnect from the connection.
```{r}
# clean up
dbDisconnect(con)
```

