---
title: "PM566-lab09-Tiansheng-Jin"
author: "Tiansheng Jin"
date: "`r Sys.Date()`"
output: 
  html_document: default
  pdf_document: default
  word_document: default
  github_document:
    html_preview: false
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
```

```{r}
library(parallel)
```

# Problem 2
## 1.This function generates a n x k dataset with all its entries distributed poission with mean lambda.
```{r}

set.seed(156)

fun1 <- function(n = 100, k = 4, lambda = 4) {
  x <- NULL
  
  for (i in 1:n)
    x <- rbind(x, rpois(k, lambda))
  
  return(x)
}
f1 <- fun1(100, 4)
mean(f1)
f1 <- fun1(1000, 4)
f1 <- fun1(10000, 4)
f1 <- fun1(50000, 4)

fun1alt <- function(n = 100, k = 4, lambda = 4) {
  x <- matrix(rpois(n*k, lambda) , ncol = 4)
}

# Benchmarking
microbenchmark::microbenchmark(
  fun1(),
  fun1alt()
)
```

## 2.Find the column max (hint: Checkout the function max.col()).
```{r}
# Data Generating Process (3 x 4 matrix)
set.seed(156)
M <- matrix(runif(12), nrow=4)

# Find each column's max value
fun2 <- function(y) {
  apply(y, 2, max)
}
fun2(y=M)

fun2alt <- function(y) {
  idx <- max.col(t(y))
  idx
  # y[cbind(idx,1:4)]
}
fun2alt(y=M)

y <- matrix(rnorm(1e4), ncol = 10)

# Benchmarking
microbenchmark::microbenchmark(
  fun2(y),
  fun2alt(y)
)
```

# Problem 3: Parallelize everything

```{r}
my_boot <- function(dat, stat, R, ncpus = 1L) {
  
  # Getting the random indices
  n <- nrow(dat)
  idx <- matrix(sample.int(n, n*R, TRUE), nrow=n, ncol=R)
 
  # Making the cluster using `ncpus`
  # STEP 1: GOES HERE
  cl <- makePSOCKcluster(4)
  clusterSetRNGStream(cl, 123)
  
  # STEP 2: GOES HERE
  clusterExport(cl, c("stat", "dat", "idx"), envir = environment())
  
  # STEP 3: THIS FUNCTION NEEDS TO BE REPLACES WITH parLapply
  ans <- lapply(seq_len(R), function(i) {
    stat(dat[idx[,i], , drop=FALSE])
  })
  
  # Coercing the list into a matrix
  ans <- do.call(rbind, ans)
  
  # STEP 4: GOES HERE
  
  ans
  
}
```
## 1.Use the previous pseudocode, and make it work with parallel. Here is just an example for you to try:
```{r}
# Bootstrap of an OLS
my_stat <- function(d) coef(lm(y ~ x, data=d))

# DATA SIM
set.seed(1)
n <- 500; R <- 1e4

x <- cbind(rnorm(n)); y <- x*5 + rnorm(n)

# Checking if we get something similar as lm
ans0 <- confint(lm(y~x))
ans1 <- my_boot(dat = data.frame(x, y), my_stat, R = R, ncpus = 2L)

# You should get something like this
t(apply(ans1, 2, quantile, c(.025,.975)))
##                   2.5%      97.5%
## (Intercept) -0.1372435 0.05074397
## x            4.8680977 5.04539763
ans0
##                  2.5 %     97.5 %
## (Intercept) -0.1379033 0.04797344
## x            4.8650100 5.04883353

```

## 2.Check whether your version actually goes faster than the non-parallel version:
```{r}
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 1L))
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 2L))
```

